### 2021-06-05 README.Rmd
addy mcaddadd

- `archigos`: an abbreviated version of the Archigos data, used internally
- `atop_alliance:` directed dyad-year alliance data from ATOP
- `capitals`: a list of capitals and capital transitions for Correlates of War state system members
- `ccode_democracy`: Correlates of War state-year data with three different estimates of democracy (Varieties of Democracy, Polity, Xavier Marquez/Pemstein et al.'s "(Quick) Unified Democracy Scores").
- `cow_alliance`: directed dyad-year alliance formation data from the Correlates of War
- `cow_contdir`: Correlates of War Direct Contiguity Data (v. 3.2)
- `cow_ddy`: a full directed dyad-year data frame of Correlates of War state system members
- `cow_gw_years`: a yearly data frame including information about Correlates of War and Gleditsch-Ward states.
- `cow_igo_ndy`: non-directed dyad-year data for Correlates of War intergovernmental organizations data.
- `cow_igo_sy`: state-year data for Correlates of War intergovernmental organizations data.
- `cow_majors`: Correlates of War major powers data (version: 2016)
- `cow_mid_ddydisps`:  Directed Dyadic Dispute-Year Data with No Duplicate Dyad-Years (CoW-MID, v. 5.0)
- `cow_mid_dirdisps`: Correlates of War Militarized Interstate Dispute data (directed dyadic dispute-year, v. 5.0) 
- `cow_mid_disps`: Correlates of War Militarized Interstate Dispute data (abbreviated dispute-level, v. 5.0) 
- `cow_mindist`: the minimum distance between Correlates of War states, in kilometers, in non-directed dyad-year format (1946-2015)
- `cow_nmc`: Correlates of War National Material Capabilities data (version 5.0)
- `cow_sdp_gdp`: (Surplus and Gross) Domestic Product for Correlates of War States
- `cow_states`: Correlates of War state system membership data (version: 2016)
- `cow_trade_sy`: Correlates of War state-year trade data (version 4.0)
- `creg`: Composition of Religious and Ethnic Groups (CREG) Fractionalization/Polarization Estimates
- `gml_dirdisp`: directed dispute-year data from version 2.1.1 of the Gibler-Miller-Little inter-state dispute data.
- `gml_mid_ddydisps`:  Directed Dyadic Dispute-Year Data with No Duplicate Dyad-Years (Gibler-Miller-Little, v. 2.1.1)
- `gw_ddy`: a full directed dyad-year data frame of Gleditsch-Ward state system members
- `gw_mindist`: the minimum distance between  Gleditsch-Ward states, in kilometers, in non-directed dyad-year format (1946-2015)
- `gw_sdp_gdp`: (Surplus and Gross) Domestic Product for Correlates of War States
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)
- `hief`: Historical Index of Ethnic Fractionalization data
- `maoz_powers`: Zeev Maoz' global/regional power data
- `rugged`: Rugged/Mountainous Terrain Data
- `td_rivalries`: Thompson and Dreyer's (2012) Strategic Rivalries, 1494-2010
- `ucdp_acd`: a (not quite) dyad-year and (not quite) state-year data set on armed conflict episodes
- `ucdp_onsets`: a state-year data set of UCDP armed conflict onsets/episodes.

>>>>

- `archigos`: an abbreviated version of the Archigos data, used internally
- `atop_alliance:` directed dyad-year alliance data from ATOP
- `capitals`: a list of capitals and capital transitions for Correlates of War state system members
- `ccode_democracy`: Correlates of War state-year data with three different estimates of democracy (Varieties of Democracy, Polity, Xavier Marquez/Pemstein et al.'s "(Quick) Unified Democracy Scores").
- `cow_alliance`: directed dyad-year alliance formation data from the Correlates of War
- `cow_contdir`: Correlates of War Direct Contiguity Data (v. 3.2)
- `cow_ddy`: a full directed dyad-year data frame of Correlates of War state system members
- `cow_gw_years`: a yearly data frame including information about Correlates of War and Gleditsch-Ward states.
- `cow_igo_ndy`: non-directed dyad-year data for Correlates of War intergovernmental organizations data.
- `cow_igo_sy`: state-year data for Correlates of War intergovernmental organizations data.
- `cow_majors`: Correlates of War major powers data (version: 2016)
- `cow_mid_ddydisps`:  Directed Dyadic Dispute-Year Data with No Duplicate Dyad-Years (CoW-MID, v. 5.0)
- `cow_mid_dirdisps`: Correlates of War Militarized Interstate Dispute data (directed dyadic dispute-year, v. 5.0) 
- `cow_mid_disps`: Correlates of War Militarized Interstate Dispute data (abbreviated dispute-level, v. 5.0) 
- `cow_mindist`: the minimum distance between Correlates of War states, in kilometers, in non-directed dyad-year format (1946-2015)
- `cow_nmc`: Correlates of War National Material Capabilities data (version 5.0)
- `cow_sdp_gdp`: (Surplus and Gross) Domestic Product for Correlates of War States
- `cow_states`: Correlates of War state system membership data (version: 2016)
- `cow_trade_sy`: Correlates of War state-year trade data (version 4.0)
- `creg`: Composition of Religious and Ethnic Groups (CREG) Fractionalization/Polarization Estimates
- `gml_dirdisp`: directed dispute-year data from version 2.1.1 of the Gibler-Miller-Little inter-state dispute data.
- `gml_mid_ddydisps`:  Directed Dyadic Dispute-Year Data with No Duplicate Dyad-Years (Gibler-Miller-Little, v. 2.1.1)
- `gw_ddy`: a full directed dyad-year data frame of Gleditsch-Ward state system members
- `gw_mindist`: the minimum distance between  Gleditsch-Ward states, in kilometers, in non-directed dyad-year format (1946-2015)
- `gw_sdp_gdp`: (Surplus and Gross) Domestic Product for Correlates of War States
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)
- `gwcode_democracy`: Gleditsch-Ward state-year data with three different estimates of democracy (Varieties of Democracy, Polity, Xavier Marquez/Pemstein et al.'s "(Quick) Unified Democracy Scores").
- `hief`: Historical Index of Ethnic Fractionalization data
- `maoz_powers`: Zeev Maoz' global/regional power data
- `rugged`: Rugged/Mountainous Terrain Data
- `td_rivalries`: Thompson and Dreyer's (2012) Strategic Rivalries, 1494-2010
- `ucdp_acd`: a (not quite) dyad-year and (not quite) state-year data set on armed conflict episodes
- `ucdp_onsets`: a state-year data set of UCDP armed conflict onsets/episodes.
